---
title: "CS 329E Data Visualization R Project 1"
author: "Nur Syairah Mohd Ridzuan, Madeline Packard, Arthur DeVitalis"
date: "February 4th, 2015"
output: html_document
---


In this project, we will go through the steps necessary to reproduce visualizations from data frames pulled from Oracle.

### Pulling Data Frames
Here, we pull four different data frames from the given orders schema. Notice how each data frame is saved, and then called with the head() function.

```{r, message=FALSE}
source("../01 Data/created_dataframe.R", echo = TRUE)
```

```{r, message=FALSE}
head(customer_df)
```

```{r, message=FALSE}
head(items_df)
```

```{r, message=FALSE}
head(order_details_df)
```

```{r, message=FALSE}
head(orders_df)
```

### Visual Representations
We can use ggplot to display the dataframes in various kinds of visualizations. 

```{r}
source("../02 Visualizations/customerdf_plot.R", echo = TRUE)
```

This graph displays the possibility that city and state has many-to-many relationship due to the existence of Fairfield in both IA and NJ.  

```{r}
source("../02 Visualizations/itemsdf_plot.R", echo = TRUE)
```

From this graph, it can be inferred that the competitive unit price for artists to sell their albums falls between 16 and 17 dollars per album.

```{r}
source("../02 Visualizations/orderdetailsdf_plot.R", echo = TRUE)
```

This histogram indicates the popularity of each item sold with the quantity shown on y-axis. It can be inferred that the album with item_id 1 is the highest selling product.

```{r}
source("../02 Visualizations/ordersdf_plot.R", echo = TRUE)
```

This graph may indicate the customer loyalty based on the frequency of each customer purchasing albums from this company.


## Reproducing the graphs displayed in step 10

First, we need to combine all the data frames above. This is done by inserting the following SQL command 'select * from orders o join customers c on o.customer_id = c.customer_id join order_details d on o.order_id = d.order_id join items i on d.item_id = i.item_id' inside RestfulREL call. The resulting call is as follows:
  
```{r, warning=FALSE}
source("../01 Data/allcombine_df.R", echo = TRUE)
```

Create a subset of `combine_df` containing the following vectors: ORDER DATE, SHIPPED DATE, UNIT PRICE, CUSTOMER_STATE
```{r, warning=FALSE}
source("../01 Data/subset_unitprice.R", echo = TRUE)
```

```{r, warning=FALSE}
#view the new data frame created from the subset
head(shipped_byunitprice)
```

Notice that in `shipped_byunitprice` data frame, ORDER DATE and SHIPPED DATE contain details that we do not need to create the graph, which are the time of order as well as the time in which the item got shipped. In order to eliminate these details, reformat ORDER DATE and SHIPPED DATE using `as.Date` function. This can be done when creating a visual representation using `ggplot2` package:

```{r, warning=FALSE}
source("../02 Visualizations/shipped_byunitprice.R", echo = TRUE)
```

Repeat the steps to produce the latter two graphs.

```{r, warning=FALSE}
source("../01 Data/subset_title.R", echo = TRUE)
```

```{r, warning=FALSE}
head(shipped_bytitle)
```

```{r, warning=FALSE}
source("../02 Visualizations/shipped_bytitle.R", echo = TRUE)
```

```{r, warning=FALSE}
source("../01 Data/subset_artist.R", echo = TRUE)
```

```{r, warning=FALSE}
head(shipped_byartist)
```

```{r, warning=FALSE, include=TRUE}
source("../02 Visualizations/shipped_byartist.R", echo = TRUE)
```







